Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-01-11 template.tex
update all the way to integral 3, trying to conclude the problem

\documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{makecell}
\usepackage{siunitx}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

\title{Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Analytic Askaryan Signals}

@@

S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2}

@@

The parameter $\gamma$ is the \textit{decay constant}, and the parameter $f_0$ is the resonance frequency.  Note that the envelope of $r(t)$, $|r_a(t)|$, is simply $R_0 \exp(-\gamma t)$, as it should be.
\item The analytic signal and response convolution inside the magnitude on the right hand side of Eq. \ref{eq:awesome} can be broken into real and imaginary parts of $s_a(t)$:

@@

r_a (t) * s_a(t) = & \\ 
& r_a(t) * \Re\lbrace s_a(t)\rbrace + \\ 
& j r_a(t) * \Im\lbrace s_a(t)\rbrace

@@

Let $\gamma' = \sqrt{2}\sigma_t \gamma$, $f_0' = \sqrt{2} \sigma_t f_0$, and $z_0 = \gamma' - 2\pi j f_0'$.  The result for $r_a(t) * \Re\lbrace s_a(t)\rbrace$ is

@@

r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 R_0 \sigma_t^2 e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} \label{eq:result1} \\
Q(z_0) &= e^{z_0^2/4} \erfc(z_0/2) \label{eq:result2}

@@

\item The result for $r_a(t) * \Im\lbrace s_a(t)\rbrace$ is

@@

r_a(t) * \Im\lbrace s_a(t)\rbrace = -\sqrt{\frac{\pi}{2}} R_0 E_0 \sigma_t t e^{-\frac{1}{2}(t/\sigma_t)^2} Q(z_0) \label{eq:result3}

@@

Note that the complementary error function and Gaussian functions are \textit{entire functions}, so $dQ/dz_0$ is defined for all $z_0$.
\item The results in Eqs. \ref{eq:result1}-\ref{eq:result3} may be expressed in terms of $s(t)$ and $r_{\rm a}(t)$:

@@

r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \\
r_a(t) * \Im\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0)

@@

\item The convolution $r_a (t) * s_a(t)$ is therefore
r_a (t) * s_a(t) = -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \\ + j\sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0)
\item The envelope of the convolution of $s(t)$ and $r(t)$ is therefore

@@

\mathcal{E}_{r * s}(t) = \frac{1}{2}|r_{\rm a}(t) * s_{\rm a}(t)|

@@

This result can be further simplified.

>>>>

\documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{empheq}
\usepackage{siunitx}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator\erf{erf}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

\title{Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals}

@@

S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} \label{eq:spec}

@@

The parameter $\gamma$ is the \textit{decay constant}, and the parameter $f_0$ is the resonance frequency.  Note that the envelope of $r(t)$, $|r_a(t)|$, is simply $R_0 \exp(-\gamma t)$, as it should be.  The proof of Eq. \ref{eq:ra} is as follows:

@@

r(t) &= R_0 e^{-\gamma t} \cos(2\pi f_0 t) \\
R(f) &= \frac{R_0}{2\pi j} \left( \frac{f - \frac{j\gamma}{2\pi}}{(f-z_+)(f-z_-)} \right) \\
z_+ &= f_0 + \frac{j\gamma}{2\pi} \\
z_- &= -f_0 + \frac{j\gamma}{2\pi} \\
\widehat{r}(t) &= \mathcal{F}^{-1}\left \lbrace - j \sgn(f) R(f) \right \rbrace \label{eq:rh} \\ 
\widehat{r}(t) &= \frac{R_0}{2j}\left( e^{2\pi j f_0 t} - e^{-2\pi j f_0 t} \right) e^{-\gamma t} \\
\widehat{r}(t) &= R_0 \sin(2\pi f_0 t) e^{-\gamma t} \\
r_a (t) &= R_0 \left(\cos(2\pi f_0 t) + j\sin(2\pi f_0 t)\right) e^{-\gamma t} \\
r_a (t) &= R_0 e^{2\pi j f_0 t} e^{-\gamma t}

@@

In evaluating the inverse Fourier transform in Eq. \ref{eq:rh}, the poles at $z_+$ and $z_-$ must be enclosed in separate contour integrals.
\item Equation \ref{eq:awesome} will now be applied, using the definition of $r_a(t)$ and the Fourier transform of $s(t)$, $S(f)$.  The Fourier transform of $r_a(t) * s_a(t)$ is $R_a(f) S_a(f)$.  Using the definition of the analytic signal, we have
R_a(f) S_a(f) = R_a(f)(1 + \sgn(f)) S(f) \label{eq:midway}
The Fourier transform of $r_a(t)$ is

@@

R_a(f) &= \frac{R_0}{2\pi j} \frac{1}{f-z} \\
z &= f_0 + \frac{j\gamma}{2\pi}

@@

The Fourier transform $S(f)$ is given by Eq. \ref{eq:spec}.  Inserting the spectra into Eq. \ref{eq:midway} and taking the inverse Fourier transform should give $r_a(t) * s_a(t)$.  Note the inverse transform integral is only over positive frequencies, due to the $1+\sgn(f)$ factor.  Introducing the time derivative removes a factor of $(2\pi j f)$ from the numerator of the integrand.  The result is
r_a(t) * s_a(t) = \\ -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{d}{dt} \int_0^\infty \frac{e^{2\pi j ft} e^{-\frac{1}{2}\left(\frac{f}{\sigma_f}\right)^2}}{f-z}df
Completing the square in the exponent, and letting $x = t/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find
r_a(t) * s_a(t) &= -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{dI_1}{dt} \\
I_1 &= e^{-x^2} \int_0^\infty \frac{e^{-(y-j x)^2}}{y-z} dy
The time derivative can be switched to a derivative with respect to $x$:

@@

\boxed{
r_a(t) * s_a(t) = -j \frac{R_0 E_0 \sigma_t^2}{\sqrt{\pi}} \frac{dI_1}{dx}}

@@

Evaluating the derivative $dI_1/dx$ gives
\frac{dI_1}{dx} = 2j e^{-x^2} \int_0^{\infty} \frac{y e^{-(y-jx)^2}}{y-z}dy + 2 x I_1 - 2 x I_1
The final two terms cancel, and the result is

@@

\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I_2(x,z)} \\
\Aboxed{I_2(x,z) &= \int_0^{\infty} \frac{y e^{-(y-jx)^2}}{y-z} dy}

@@

\item Note that $I_2(x,0)$ has an exact solution:
I_2(x,0) &= \frac{\sqrt{\pi}}{2}(1+\erf(jx)) \\
I_2(x,0) &= \frac{\sqrt{\pi}}{2} + j e^{x^2} D(x)
However, approximating $I_2(x,z) \approx I_2(x,0)$ drops the dependance on $\gamma$ and $f_0$.  This suggests expanding $I_2(x,z)$ in a Taylor series about $z=0$:
I_2(x,z) &\approx I_2(x,0) + \sum_{n=1}^{\infty} z^n I_3(x,n) \\
I_3(x,n) &= \int_0^{\infty} y^{-n} e^{-(y-jx)^2} dy \\
I_3(x,n) &= \int_0^{\infty} y^{-n} e^{(x+jy)^2} dy
For example, when the lower limit is restricted from 0 to just $z$, the term $I(0,1)$ is

@@

I(0,1) = \int_z^{\infty} y^{-1} e^{-y^2} dy = \frac{1}{2}E_1(z)

@@
